Locus Statistics

### 2017-06-30 doc/RMD/locus-stats.Rmd
update locus-stats to use syd's preferred *h*

```{r}
library("poppr")
load(file.path(PROJHOME, "data", "sclerotinia_16_loci.rda"))
```

@@

ranges <- map_chr(alleles(dat11), makerange)
ranges <- c(ranges, alleles(dat11) %>% unlist(use.names = FALSE) %>% makerange)
locus_table(dat11, information = FALSE) %>% 
  as.data.frame() %>%
  rownames_to_column("Locus") %>%
  mutate(Locus = gsub("\\([FH]\\)", "", Locus)) %>%
  add_column(Range = ranges) %>%
  select(Locus, Range, allele, Hexp, Evenness) %>%
  mutate(allele = round(allele, 2)) %>%
  rename(`$H_{exp}$` = Hexp, `No. alleles` = allele) %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>%
  huxtable::set_number_format(1:12, 3, 0) %>%
  huxtable::set_number_format(everywhere, 4:5, 2) %>%
  huxtable::set_align(everywhere, 3:5, "right") %>%
  huxtable::set_col_width(c(0.06, 0.07, 0.123, 0.09, 0.08)) %>%
  huxtable::print_md(max_width = 47)
```

>>>>

```{r}
library("tidyverse")
library("poppr")
load(file.path(PROJHOME, "data", "sclerotinia_16_loci.rda"))
```

@@

ranges <- map_chr(alleles(dat11), makerange)
ranges <- c(ranges, alleles(dat11) %>% unlist(use.names = FALSE) %>% makerange)
locus_table(dat11, information = FALSE) %>% 
  as.data.frame() %>%
  rownames_to_column("Locus") %>%
  mutate(Locus = gsub("\\([FH]\\)", "", Locus)) %>%
  add_column(Range = ranges) %>%
  select(Locus, Range, allele, Hexp, Evenness) %>%
  mutate(allele = round(allele, 2)) %>%
  rename(`*h*` = Hexp, `No. alleles` = allele) %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>%
  huxtable::set_number_format(1:12, 3, 0) %>%
  huxtable::set_number_format(huxtable::everywhere, 4:5, 2) %>%
  huxtable::set_align(huxtable::everywhere, 3:5, "right") %>%
  huxtable::set_col_width(c(0.06, 0.07, 0.12, 0.06, 0.09)) %>%
  huxtable::print_md(max_width = 47)
```
